---
title: "Testing plan"
author: "Svetlana Koroteeva"
date: "`r Sys.Date()`"
output: 
  html_document:
    self_contained: false
    keep_md: true
    path: "vignettes/Testing_plan.html"
vignette: >
  %\VignetteIndexEntry{Testing plan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Testing Plan

## Automated Tests

Set of automated unit tests is included to the package. 

## `testthat`

The unittests are implemented using the `testthat` framework. To run the tests, load MusicFeatClassR, and then use the `test_dir()` or `test_file()` functions provided by `testthat`. For example:


```{r,  warning=FALSE}
library(MusicFeatClassR)
library(testthat)
current_dir<-getwd()
root_dir<-dirname(current_dir)
test_dir(file.path(root_dir,"tests"))
```

This will execute all the tests. Note: there are could be warnings related to packages.

## Interpreting the Results

After running the tests, testthat will give a summary of test results, which tests are passed and failed.

## Writing New Tests

New tests could be placed in "tests" folder.

## Continuous Integration

Run the tests whenever changes are made for the package.

